A Software Engineering Perspective on \\ OpenMP and PThreads

### 2017-08-08 sections/05-responses.tex
Edit section on APIs

This shows that the perceptions of usability and performance improvement
regarding \textit{OpenMP} did not reflect in the actual implementations and
submissions. We believe that \textit{OpenMP} is still not as easy as it appears
to be, and that the students' responses strengthen the argument for teaching
lower-level technologies for parallel and distributed computing.

>>>>

This shows that the perceptions of usability and performance improvement
regarding \textit{OpenMP} did not reflect in the actual implementations and
submissions. We assert that \textit{OpenMP} is still not as easy as it appears
to be, and that the students' responses strengthen the argument for teaching
lower-level technologies for parallel and distributed computing.
